Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-07 Paper/grass.tex

\documentclass[aps,prl,reprint,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1}  % for review and submission
%\documentclass[aps,twocolumn,floatfix,prl,10pt]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
%\documentclass[aps,preprint,floatfix,prl]{revtex4-1}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{color}
\usepackage{longtable}
\usepackage{array}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

@@

\begin{figure}
\includegraphics[]{Asymptotic_noshear}
\caption{Plot of mode shape $|\phi|$ for different shear layer thickness in limit of small shear layer thickness 
for representative values of grass density. Mode 1 is shown in solid and Mode 2 is shown in dashed. 
The parameters Mode 2 shapes are chosen such that $\Rey \gg 1$, $\Ndg \gg 1$ (specifying in terms of $\delta/H$) 
but $\Rey/\Ndg = O(1)$. The mode shapes approach each other for these small values of $\delta/H$ indicating that 
the large grass density asymptote is reached. Mode 2 shapes appear self-similar in shape as $\delta\to 0$, 
and are compared to each other on a rescaled coordinate in the inset. Inset shows $|\phi|$ for 
Mode 1 as a function of $(y-\hg)/\delta$. The modes approach a universal shape, indicating that an asymptotic limit 
has been reached. The limit is not yet reached for the case $\delta/H = 0.05$ due to the influence of bottom boundary; 
the grass height in this case is comparable to the boundary layer thickness.}
\label{Asymptotic_mode}
\end{figure}

On the other hand, Mode 1 asymptotically localizes to the boundary layer near the grass tip, and exhibits a different asymptotic behavior with $k \sim O(H/\delta)$, and $\Rey \sim (H/\delta)$ (or $\Rey \propto {\Ndg}^{1/2}$) at the threshold. 
This limit can be understood through asymptotically estimating the sizes of the terms in \eqref{Orr-somerfield} using $D\sim \delta^{-1}$, $\sigma \sim \delta^{-1}$, and $U\sim \delta$; the magnitude of the advection term is $\Rey/\delta^3 \sim \Rey^2 \Ndg $, and the viscous term (or the vegetation drag term, which is found to scale identically) in the boundary layer is $\delta^{-4} \sim (\Rey \Ndg)^{4/3}$. The terms balance when $\Rey \sim {\Ndg}^{1/2}$ (or $\Rey \sim H/\delta$), explaining the numerically observed asymptote (see figure \ref{Re_vs_delta}). This analysis predicts that the mode structure is self-similar over the length scale $\delta$; the verification of this expectation is shown in figure \ref{Asymptotic_mode}, supporting this argument.

>>>>

\documentclass[aps,prl,reprint,twocolumn,showpacs,superscriptaddress,10pt]{revtex4-1}  % for review and submission
%\documentclass[aps,twocolumn,floatfix,prl,10pt]{revtex4-1}
%\documentclass[letterpaper,10pt,prl,twocolumn,aps]{revtex4-1}
%\documentclass[aps,preprint,floatfix,prl]{revtex4-1}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{color}
\usepackage{longtable}
\usepackage{array}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

@@

\begin{figure}
\includegraphics[]{Asymptotic_noshear}
\caption{Plot of mode shape $|\phi|$ for different shear layer thickness in limit of small shear layer thickness for representative values of grass density. 
Mode 1 is shown in solid and Mode 2 is shown in dashed. The parameters Mode 2 shapes are chosen such that $\Rey \gg 1$, $\Ndg \gg 1$ (specified in terms of $\delta/H$) but $\Rey/\Ndg = O(1)$. 
The mode shapes approach each other for these small values of $\delta/H$ indicating that the large grass density asymptote is reached. Mode 1 shapes appear self-similar in shape as $\delta\to 0$, 
and are compared to each other on a rescaled coordinate in the inset. 
Inset shows $|\phi|$ for Mode 1 as a function of $(y-\hg)/\delta$. The modes approach a universal shape, indicating that an asymptotic limit has been reached. 
The limit is not yet reached for the case $\delta/H = 0.01$ due to the influence of bottom boundary; the grass height in this case is comparable to the boundary layer thickness.}
\label{Asymptotic_mode}
\end{figure}

On the other hand, Mode 1 asymptotically localizes to the boundary layer near the grass tip, and exhibits a different asymptotic behavior with $k \sim O(H/\delta)$, and $\Rey \sim (H/\delta)$ (or $\Rey \propto {\Ndg}^{1/2}$) at the threshold.

This limit can be understood through asymptotically estimating the sizes of the terms in \eqref{Orr-somerfield} using $D\sim \delta^{-1}$, $\sigma \sim \delta^{-1}$, and $U\sim \delta$; the magnitude of the advection term is $\Rey/\delta^3 \sim \Rey^2 \Ndg $, and the viscous term (or the vegetation drag term, which is found to scale identically) in the boundary layer is $\delta^{-4} \sim (\Rey \Ndg)^{4/3}$. The terms balance when $\Rey \sim {\Ndg}^{1/2}$ (or $\Rey \sim H/\delta$), explaining the numerically observed asymptote (see figure \ref{Re_vs_delta}). This analysis predicts that the mode structure is self-similar over the length scale $\delta$; the verification of this expectation is shown in figure \ref{Asymptotic_mode}, supporting this argument.
